\subsection*{Compile error in C/\+C++}

\subsubsection*{Error occurs when compiling csim\+\_\+shared}

Codes might not be compiled with gcc/g++ ver$>$=7. Please check codes are compiled with gcc and g++ and it\textquotesingle{}s version is greater or equal to 7.\+0.\+0.

For Mac\+OS Users\+: the default backend of gcc/g++ command is clang, which is not supported in Qulacs.

\subsubsection*{When we compile Qulacs with mingw, compiler says header files such as crypt.\+h or sys/select.\+h was not found. When objects are linked, linker says library -\/lintl was not found.}

This may occur when you try to build 32bit python library with 64bit compiler, or 64bit lib with 32bit. When you compile C++ with 32bit/64bit, the python library must be 32bit/64bit, respectively.

\subsection*{Error in python library}

\subsubsection*{I have many versions of python, and want to build Qulacs for specific one.}

Qulacs is build for default python and python-\/config. Please set the version where you want to install Qulacs as a default using pyenv or conda. We can also specify python binary when we do cmake by adding -\/D P\+Y\+T\+H\+O\+N\+\_\+\+E\+X\+E\+C\+U\+T\+A\+B\+LE\+:F\+I\+L\+E\+P\+A\+TH=/usr/bin/pythonx.x.

\subsection*{When I import library, python says there is no init function.}

If you use Qulacs from python and call functions directly using dll/pyd, the name of python library must not be changed. If you change the dll/pyd name of python library, you will see this error.

If you import python dll/pyd which is build for different python version, you may see this error.

\subsubsection*{Segmentation fault occurs when I import library. Python immediately exit after importing library. Python says functions starting with \char`\"{}\+Py\+\_\+\char`\"{} was not found. Though there exists dll files, python says there is no dll/pyd.}

If you import python dll/pyd which is build for different version python, you see these errors. Error messages depend on the python version. 